---
title: "MCDS.exe Testing"
author: "Laura Marshall"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes: \usepackage{booktabs}
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
library(kableExtra)
library(Distance)
library(gt)

knitr::opts_chunk$set(echo = TRUE)
re_eval <- FALSE

source("Support.R")
```

## Things outstanding in mrds

In addition to the notes throughout this document the following also
needs further work or investigations:

-   **FIXED** Issue 83 in mrds relating to factor ordering differences
    between mrds and MCDS
    (<https://github.com/DistanceDevelopment/mrds/issues/83>)

-   **Now seems to spot and display warnings and errors from MCDS** Reading in and processing the warnings and / or errors in the log
    file generated by MCDS - What do we do about cases where mcds.exe
    fits with negative pdf? E.g.
    <https://github.com/DistanceDevelopment/Distance/issues/160>

-   Do the monotonicity constraints get passed to MCDS correctly? **YES**

-   Check the passing of parameter starting values to MCDS - also
    potential issues here regarding factor ordering! **Now passing parameter start values - no problems with factor ordering as this is dealt with by the reordering of the factor names passed to MCDS**

-   **Made errors into non fatal warnings and messages**

-   Check the passing of parameter bound to MCDS. Note this can only be done via mrds NOT via
    Distance. Low priority - not done
    
-   Could do with more tests of the case of uniform only models to check that abundance estimates are correctly calculated.

\newpage

## Capercaillie Data

Various warnings and errors that want further investigation:
```{r warn_capercaillie, eval = re_eval}
# MCDS warning - does this want removed?
# ** Warning: One or more cluster sizes are coded as -1. Distance assumes -1 to mean a cluster of undetermined size. These observations are used for estimating detection probability and encounter rate, but not cluster size. **

```


```{r capercaillie, eval = re_eval}
data("capercaillie")

model.compare <- test.models(capercaillie, 
                             truncation = max(capercaillie$distance), 
                             transect = "line", 
                             convert.units = 10)

save(model.compare, file = "results/capercaillie.ROBJ")

```

```{r capercaillie_results, echo = FALSE}
load(file = "results/capercaillie.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Capercaillie data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Cue Counting Data

Things that might want further investigation:

-   Nhat for the hn herm 1 model is \~14% higher for the MCDS optimised
    model than the R optimised model

-   Why is the lnl_R value for the hr poly 2 model negative? This has now changed!

Various warnings and errors that want further investigation:
```{r warn_cuecount, eval = re_eval}
# Fitting hazard-rate key function with simple polynomial(4,6) adjustments
# ** Warning: One or more cluster sizes are coded as -1. Distance assumes -1 to mean a cluster of undetermined size. These observations are used for estimating detection probability and encounter rate, but not cluster size. **
# Warning: Detection function is not strictly monotonic!Warning: Detection function is less than 0 at some distancesWarning: Detection function is not strictly monotonic!
# Warning: Detection function is less than 0 at some distancesAIC= -0.103
# Fitting half-normal key function with Hermite(4,6) adjustments
# ** Warning: One or more cluster sizes are coded as -1. Distance assumes -1 to mean a cluster of undetermined size. These observations are used for estimating detection probability and encounter rate, but not cluster size. **
# ** Warning: convergence failure **
# Warning in check.mono(result, n.pts = control$mono.points) :
#   Detection function is not strictly monotonic!
# Warning in check.mono(result, n.pts = control$mono.points) :
#   Detection function is not strictly monotonic!
# AIC= -1.752
# Warning in mrds::check.mono(model, n.pts = 20) :
#   Detection function is not strictly monotonic!
# No survey area information supplied, only estimating detection function.
# 
# Fitting half-normal key function with Hermite(4,6) adjustments
# ** Warning: One or more cluster sizes are coded as -1. Distance assumes -1 to mean a cluster of undetermined size. These observations are used for estimating detection probability and encounter rate, but not cluster size. **
# ** Warning: convergence failure **
# Warning in check.mono(result, n.pts = control$mono.points) :
#   Detection function is not strictly monotonic!
# AIC= 1.966
# No survey area information supplied, only estimating detection function.
```

```{r cuecounting, eval = re_eval}
data("CueCountingExample")

model.compare <- test.models(CueCountingExample, 
                             truncation = max(CueCountingExample$distance, na.rm = TRUE), 
                             transect = "point")

save(model.compare, file = "results/cue_counting.ROBJ")

```

```{r cuecounting_results, echo = FALSE}
load(file = "results/cue_counting.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for cue counting data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Ducknest Data

Things that might want further investigation:


-   p_MCDS is 1 for a few of these models and when it is, it is
    estimating Nhat much lower than the R optimiser.
    
```{r warn_ducknest}
# Fitting half-normal key function with Hermite(4,6) adjustments
# Warning: First partial hessian is singular and second-partial hessian is NULL, no hessian
# AIC= 932.07
# No hessian, possible numerical problems; only estimating detection function.
```

```{r ducknest, eval = re_eval}
data("ducknest")

model.compare <- test.models(ducknest, 
                             truncation = max(ducknest$distance, na.rm = TRUE), 
                             transect = "line")

save(model.compare, file = "results/ducknest.ROBJ")

```

```{r ducknest_results, echo = FALSE}
load(file = "results/ducknest.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Ducknest data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## DuikerCameraTraps

Things that might want further investigation: 
- Nhat values look to differ by around 20% between the two optimisers

    
```{r warn_duiker}
# Fitting half-normal key function with Hermite(4,6) adjustments
# Warning: First partial hessian is singular; using second-partial hessian
# Warning: First partial hessian is singular; using second-partial hessian
# AIC= 25014.184
# Error in array(x, c(length(x), 1L), if (!is.null(names(x))) list(names(x),  : 
#   'data' must be of a vector type, was 'NULL'
# Error in t(partial) %*% vcov : 
#   requires numeric/complex matrix/vector arguments
```

```{r duiker, eval = re_eval}
data("DuikerCameraTraps")

model.compare <- test.models(DuikerCameraTraps,
                             truncation = list(left = 2, right = 15),
                             cutpoints = c(seq(2,8,1), 10, 12, 15),
                             transect = "point")

save(model.compare, file = "results/DuikerCameraTraps.ROBJ")

```

```{r duiker_results, echo = FALSE}
load(file = "results/DuikerCameraTraps.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Duiker camera trap data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## LTExercise Data

Things that might want further investigation: - - Why is is warning
about "Warning in process.data(data, meta.data, check = FALSE) : no
truncation distance specified; using largest observed distance"?

```{r LTExercise, eval = re_eval}
data("LTExercise")

model.compare <- test.models(LTExercise,
                             truncation = max(LTExercise$distance, na.rm = TRUE),
                             transect = "line")

save(model.compare, file = "results/LTExercise.ROBJ")

```

```{r LTExercise_results, echo = FALSE}
load(file = "results/LTExercise.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for LTExercise data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## PTExercise Data

Things that might want further investigation: - - Why is is warning
about "Warning in process.data(data, meta.data, check = FALSE) : no
truncation distance specified; using largest observed distance"?

```{r PTExercise, eval = re_eval}
data("PTExercise")

model.compare <- test.models(PTExercise,
                             truncation = max(PTExercise$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/PTExercise.ROBJ")

```

```{r PTExercise_results, echo = FALSE}
load(file = "results/PTExercise.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for PTExercise data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Savannah Sparrow 1980

Everything looks to run fine.

```{r SS19080, eval = re_eval}
data("Savannah_sparrow_1980")

model.compare <- test.models(Savannah_sparrow_1980,
                             truncation = max(Savannah_sparrow_1980$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/Savannah_sparrow_1980.ROBJ")

```

```{r SS1980_results, echo = FALSE}
load(file = "results/Savannah_sparrow_1980.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Savannah sparrow 1980 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Savannah Sparrow 1981

Everything looks to run fine.

```{r SS19081, eval = re_eval}
data("Savannah_sparrow_1981")

model.compare <- test.models(Savannah_sparrow_1981,
                             truncation = max(Savannah_sparrow_1981$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/Savannah_sparrow_1981.ROBJ")

```

```{r SS1981_results, echo = FALSE}
load(file = "results/Savannah_sparrow_1981.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Savannah sparrow 1981 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Sika Deer

Everything looks to run fine.

```{r sikadeer, eval = re_eval}
data("sikadeer")

model.compare <- test.models(sikadeer,
                             truncation = max(sikadeer$distance, na.rm = TRUE),
                             transect = "line")

save(model.compare, file = "results/sikadeer.ROBJ")

```

```{r sikadeer_results, echo = FALSE}
load(file = "results/sikadeer.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for sikadeer data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren 5 minute count

This one brings up the warning 'Detection function is less than 0 at
some distances' for quite a few of the models. This warning occured for
the last model where there is a substantial difference in abundance
estimates.

```{r wren_5min, eval = re_eval}
data("wren_5min")

model.compare <- test.models(wren_5min,
                             truncation = max(wren_5min$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/wren_5min.ROBJ")

```

```{r wren_5min_results, echo = FALSE}
load(file = "results/wren_5min.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_5min data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren cue counting

This one brings up the warning 'Detection function is less than 0 at
some distances' for quite a few of the models. This warning occured for
the last model where there is a substantial difference in abundance
estimates.

```{r wren_cuecount, eval = re_eval}
data("wren_cuecount")

model.compare <- test.models(wren_cuecount,
                             truncation = max(wren_cuecount$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/wren_cuecount.ROBJ")

```

```{r wren_cuecount_results, echo = FALSE}
load(file = "results/wren_cuecount.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_cuecount data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren line transect


```{r wren_lt, eval = re_eval}
data("wren_lt")

model.compare <- test.models(wren_lt,
                             truncation = max(wren_lt$distance, na.rm = TRUE),
                             transect = "line")

save(model.compare, file = "results/wren_lt.ROBJ")

```

```{r wren_lt_results, echo = FALSE}
load(file = "results/wren_lt.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_lt data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren snapshot

Some errors / warnings:

```{r wren_snapshot, eval = re_eval}
data("wren_snapshot")

model.compare <- test.models(wren_snapshot,
                             truncation = max(wren_snapshot$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/wren_snapshot.ROBJ")

```

```{r wren_snapshot_results, echo = FALSE}
load(file = "results/wren_snapshot.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_snapshot data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr1

Some estimates of abundance differ significantly!

```{r dathr1, eval = re_eval}
load(file = "data/dathr1.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr1.ROBJ")

```

```{r dathr1_results, echo = FALSE}
load(file = "results/dathr1.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr1 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr2

```{r dathr2, eval = re_eval}
load(file = "data/dathr2.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr2.ROBJ")

```

```{r dathr2_results, echo = FALSE}
load(file = "results/dathr2.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr2 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr3

Some errors / warnings:


```{r dathr3, eval = re_eval}
load(file = "data/dathr3.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr3.ROBJ")

```

```{r dathr3_results, echo = FALSE}
load(file = "results/dathr3.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr3 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr4

```{r dathr4, eval = re_eval}
load(file = "data/dathr4.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr4.ROBJ")

```

```{r dathr4_results, echo = FALSE}
load(file = "results/dathr4.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr4 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## rocio_dat

```{r rocio_dat, eval = re_eval}
load(file = "data/rocio_dat.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/rocio_dat.ROBJ")

```

```{r rocio_dat_results, echo = FALSE}
load(file = "results/rocio_dat.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for rocio\\_dat data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## rocio_dat2

```{r rocio_dat2, eval = re_eval}
load(file = "data/rocio_dat_2.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/rocio_dat2.ROBJ")

```

```{r rocio_dat2_results, echo = FALSE}
load(file = "results/rocio_dat2.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for rocio\\_dat2 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## amakihi

There is a very big difference in estimated abundance for the first
model here!

```{r amakihi, eval = re_eval}
data("amakihi")

model.compare <- test.cov.models(amakihi,
                             truncation = 82.5,
                             transect = "point",
                             models = list(~as.factor(OBs)+HAS+MAS, ~as.factor(OBs)+MAS, ~as.factor(OBs)+HAS))

save(model.compare, file = "results/amakihi.ROBJ")

```

```{r amakihi_results, echo = FALSE}
load(file = "results/amakihi.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for amakihi data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## akepa data

```{r akepa, eval = re_eval}
load(file = "data/akepa.RData")

model.compare <- test.cov.models(dat,
                             truncation = 58,
                             transect = "line",
                             models = list(~as.factor(Obs)))

save(model.compare, file = "results/akepa.ROBJ")

```

```{r akepa_results, echo = FALSE}
load(file = "results/akepa.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for akepa data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## ETP Dolphins

Some errors / warnings:


```{r ETP_Dolphin, eval = re_eval}
data("ETP_Dolphin")

model.compare <- test.cov.models(ETP_Dolphin,
                             truncation = max(ETP_Dolphin$distance, na.rm = TRUE),
                             transect = "line",
                             models = list(~size, ~size+Beauf.class, ~LnCluster))

save(model.compare, file = "results/ETP_Dolphin.ROBJ")

```

```{r ETP_Dolphin_results, echo = FALSE}
load(file = "results/ETP_Dolphin.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for ETP dolphin data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Minke data

```{r minke, eval = re_eval}
data("minke")

model.compare <- test.cov.models(minke,
                             truncation = max(minke$distance, na.rm = TRUE),
                             transect = "line",
                             models = list(~as.factor(Region.Label)))

save(model.compare, file = "results/minke.ROBJ")

```

```{r minke_results, echo = FALSE}
load(file = "results/minke.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for minke data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

## Cluster Exercise

```{r ClusterExercise, eval = re_eval}
data("ClusterExercise")

model.compare <- test.cov.models(ClusterExercise,
                             truncation = max(ClusterExercise$distance, na.rm = TRUE),
                             cutpoints = c(0,0.214285714285714,0.428571428571429,0.642857142857143,0.857142857142857,1.07142857142857,1.28571428571429,1.5),
                             transect = "line",
                             models = list(~size, ~Cluster.strat))

save(model.compare, file = "results/ClusterExercise.ROBJ")

```

```{r ClusterExercise_results, echo = FALSE}
load(file = "results/ClusterExercise.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for ClusterExercise data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```
