---
title: "MCDS.exe Testing"
author: "Laura Marshall"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes: \usepackage{booktabs}
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
library(kableExtra)
library(Distance)
library(gt)

knitr::opts_chunk$set(echo = TRUE)
re_eval <- FALSE

source("Support.R")
```

This report details a number of analyses which have been run using both
the default R optimiser within mrds and and also the MCDS.exe optimiser. The MCDS.exe optimiser requires manual installation by the user, see below. This document is designed to allow users to assess the differences in results between the two optimisers.

The code below can be used to install the MCDS.exe optimizer.

```{r install_MCDS, eval = FALSE, echo = TRUE}
# Install the MCDS.exe optimiser
download.file("http://distancesampling.org/R/MCDS.exe", 
              paste0(system.file(package="mrds"),"/MCDS.exe"), mode = "wb")

# Help on the optimiser can be obtained using 
?MCDS.exe
```


```{r run_time, eval = TRUE, echo = FALSE}
if(re_eval){
  run.time <- format(Sys.time(), "%H:%M %d/%m/%Y")
  save(run.time, file = "results/run_time.ROBJ")
}else{
  load("results/run_time.ROBJ")
}
cat("These results were generated at: ", run.time, fill = TRUE)
```

\newpage

## Capercaillie Data

```{r capercaillie, eval = re_eval}
data("capercaillie")

model.compare <- test.models(capercaillie, 
                             truncation = max(capercaillie$distance), 
                             transect = "line", 
                             convert.units = 10)

save(model.compare, file = "results/capercaillie.ROBJ")

```

```{r capercaillie_results, echo = FALSE}
load(file = "results/capercaillie.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Capercaillie data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Cue Counting Data

```{r cuecounting, eval = re_eval}
data("CueCountingExample")

model.compare <- test.models(CueCountingExample, 
                             truncation = max(CueCountingExample$distance, na.rm = TRUE), 
                             transect = "point")

save(model.compare, file = "results/cue_counting.ROBJ")

```

```{r cuecounting_results, echo = FALSE}
load(file = "results/cue_counting.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for cue counting data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Ducknest Data


```{r ducknest, eval = re_eval}
data("ducknest")

model.compare <- test.models(ducknest, 
                             truncation = max(ducknest$distance, na.rm = TRUE), 
                             transect = "line")

save(model.compare, file = "results/ducknest.ROBJ")

```

```{r ducknest_results, echo = FALSE}
load(file = "results/ducknest.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Ducknest data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## DuikerCameraTraps

```{r duiker, eval = re_eval}
data("DuikerCameraTraps")

model.compare <- test.models(DuikerCameraTraps,
                             truncation = list(left = 2, right = 15),
                             cutpoints = c(seq(2,8,1), 10, 12, 15),
                             transect = "point")

save(model.compare, file = "results/DuikerCameraTraps.ROBJ")

```

```{r duiker_results, echo = FALSE}
load(file = "results/DuikerCameraTraps.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Duiker camera trap data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## LTExercise Data

```{r LTExercise, eval = re_eval}
data("LTExercise")

model.compare <- test.models(LTExercise,
                             truncation = max(LTExercise$distance, na.rm = TRUE),
                             transect = "line")

save(model.compare, file = "results/LTExercise.ROBJ")

```

```{r LTExercise_results, echo = FALSE}
load(file = "results/LTExercise.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for LTExercise data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## PTExercise Data

```{r PTExercise, eval = re_eval}
data("PTExercise")

model.compare <- test.models(PTExercise,
                             truncation = max(PTExercise$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/PTExercise.ROBJ")

```

```{r PTExercise_results, echo = FALSE}
load(file = "results/PTExercise.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for PTExercise data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Savannah Sparrow 1980

```{r SS19080, eval = re_eval}
data("Savannah_sparrow_1980")

model.compare <- test.models(Savannah_sparrow_1980,
                             truncation = max(Savannah_sparrow_1980$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/Savannah_sparrow_1980.ROBJ")

```

```{r SS1980_results, echo = FALSE}
load(file = "results/Savannah_sparrow_1980.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Savannah sparrow 1980 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Savannah Sparrow 1981

```{r SS19081, eval = re_eval}
data("Savannah_sparrow_1981")

model.compare <- test.models(Savannah_sparrow_1981,
                             truncation = max(Savannah_sparrow_1981$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/Savannah_sparrow_1981.ROBJ")

```

```{r SS1981_results, echo = FALSE}
load(file = "results/Savannah_sparrow_1981.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for Savannah sparrow 1981 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Sika Deer



```{r sikadeer, eval = re_eval}
data("sikadeer")

model.compare <- test.models(sikadeer,
                             truncation = max(sikadeer$distance, na.rm = TRUE),
                             transect = "line")

save(model.compare, file = "results/sikadeer.ROBJ")

```

```{r sikadeer_results, echo = FALSE}
load(file = "results/sikadeer.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for sikadeer data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren 5 minute count


```{r wren_5min, eval = re_eval}
data("wren_5min")

model.compare <- test.models(wren_5min,
                             truncation = max(wren_5min$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/wren_5min.ROBJ")

```

```{r wren_5min_results, echo = FALSE}
load(file = "results/wren_5min.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_5min data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren cue counting

```{r wren_cuecount, eval = re_eval}
data("wren_cuecount")

model.compare <- test.models(wren_cuecount,
                             truncation = max(wren_cuecount$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/wren_cuecount.ROBJ")

```

```{r wren_cuecount_results, echo = FALSE}
load(file = "results/wren_cuecount.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_cuecount data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren line transect

```{r wren_lt, eval = re_eval}
data("wren_lt")

model.compare <- test.models(wren_lt,
                             truncation = max(wren_lt$distance, na.rm = TRUE),
                             transect = "line")

save(model.compare, file = "results/wren_lt.ROBJ")

```

```{r wren_lt_results, echo = FALSE}
load(file = "results/wren_lt.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_lt data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Wren snapshot

```{r wren_snapshot, eval = re_eval}
data("wren_snapshot")

model.compare <- test.models(wren_snapshot,
                             truncation = max(wren_snapshot$distance, na.rm = TRUE),
                             transect = "point")

save(model.compare, file = "results/wren_snapshot.ROBJ")

```

```{r wren_snapshot_results, echo = FALSE}
load(file = "results/wren_snapshot.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for wren\\_snapshot data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr1

```{r dathr1, eval = re_eval}
load(file = "data/dathr1.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr1.ROBJ")

```

```{r dathr1_results, echo = FALSE}
load(file = "results/dathr1.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr1 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr2

```{r dathr2, eval = re_eval}
load(file = "data/dathr2.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr2.ROBJ")

```

```{r dathr2_results, echo = FALSE}
load(file = "results/dathr2.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr2 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr3

```{r dathr3, eval = re_eval}
load(file = "data/dathr3.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr3.ROBJ")

```

```{r dathr3_results, echo = FALSE}
load(file = "results/dathr3.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr3 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## dathr4

```{r dathr4, eval = re_eval}
load(file = "data/dathr4.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/dathr4.ROBJ")

```

```{r dathr4_results, echo = FALSE}
load(file = "results/dathr4.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for dathr4 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## rocio_dat

```{r rocio_dat, eval = re_eval}
load(file = "data/rocio_dat.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/rocio_dat.ROBJ")

```

```{r rocio_dat_results, echo = FALSE}
load(file = "results/rocio_dat.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for rocio\\_dat data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## rocio_dat2

```{r rocio_dat2, eval = re_eval}
load(file = "data/rocio_dat_2.RData")

model.compare <- test.models(dat,
                             truncation = 30,
                             transect = "point")

save(model.compare, file = "results/rocio_dat2.ROBJ")

```

```{r rocio_dat2_results, echo = FALSE}
load(file = "results/rocio_dat2.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for rocio\\_dat2 data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## amakihi

```{r amakihi, eval = re_eval}
data("amakihi")

model.compare <- test.cov.models(amakihi,
                             truncation = 82.5,
                             transect = "point",
                             models = list(~as.factor(OBs)+HAS+MAS, 
                                           ~as.factor(OBs)+MAS, 
                                           ~as.factor(OBs)+HAS))

save(model.compare, file = "results/amakihi.ROBJ")

```

```{r amakihi_results, echo = FALSE}
load(file = "results/amakihi.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for amakihi data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## akepa data

```{r akepa, eval = re_eval}
load(file = "data/akepa.RData")

model.compare <- test.cov.models(dat,
                             truncation = 58,
                             transect = "line",
                             models = list(~as.factor(Obs)))

save(model.compare, file = "results/akepa.ROBJ")

```

```{r akepa_results, echo = FALSE}
load(file = "results/akepa.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for akepa data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## ETP Dolphins

```{r ETP_Dolphin, eval = re_eval}
data("ETP_Dolphin")

model.compare <- test.cov.models(ETP_Dolphin,
                             truncation = max(ETP_Dolphin$distance, na.rm = TRUE),
                             transect = "line",
                             models = list(~size, ~size+Beauf.class, ~LnCluster))


save(model.compare, file = "results/ETP_Dolphin.ROBJ")

```

```{r ETP_Dolphin_results, echo = FALSE}
load(file = "results/ETP_Dolphin.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for ETP dolphin data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

\newpage

## Minke data

```{r minke, eval = re_eval}
data("minke")

model.compare <- test.cov.models(minke,
                             truncation = max(minke$distance, na.rm = TRUE),
                             transect = "line",
                             models = list(~as.factor(Region.Label)))

save(model.compare, file = "results/minke.ROBJ")

```

```{r minke_results, echo = FALSE}
load(file = "results/minke.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for minke data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```

## Cluster Exercise

```{r ClusterExercise, eval = re_eval}
data("ClusterExercise")

model.compare <- test.cov.models(ClusterExercise,
                             truncation = max(ClusterExercise$distance, na.rm = TRUE),
                             cutpoints =c(0,0.214285714285714,0.428571428571429,
                                        0.642857142857143,0.857142857142857,
                                        1.07142857142857,1.28571428571429,1.5),
                             transect = "line",
                             models = list(~size, ~Cluster.strat))

save(model.compare, file = "results/ClusterExercise.ROBJ")

```

```{r ClusterExercise_results, echo = FALSE}
load(file = "results/ClusterExercise.ROBJ")

knitr::kable(model.compare,
             format = "latex",
             caption = "Comparison of R and MCDS model fits for ClusterExercise data. key - key function, adj - type of adjustment term, nadj - number of adjustments, lnl\\_R - likelihood value for R optimiser, lnl\\_MCDS - likelihood value for MCDS optimiser, optimizer - the selected optimiser, p\\_R the estimated average probability of detection for the R optimised model, p\\_MCDS the estimated average probability of detection for the MCDS optimised model, Nhat\\_R - estimated abundance in covered region from R optimised model, Nhat\\_MCDS - estimated abundance in covered region from MCDS optimised model.",
             booktabs = TRUE,
             longtable = FALSE) %>%
  kable_styling(latex_options = "HOLD_position")

```
